\section{Work Experience}
\subsection{Open-Source Software Developer}{GitHub}{Jun. 2017 - \textit{Present}}
\begin{itemize}
    \item Contributed to Linux desktop and server integration, collaborating with over 1000 global developers to enhance the Linux kernel 6.x.
    \item Led efforts to improve NVIDIA open-source drivers, incorporating support for G-Sync and RayTracing, and enabling advanced gaming features with Steam’s Proton framework.
    \item Demonstrated expertise in system-level programming with C and emerging Rust frameworks for enhanced security and performance in open-source environments.
\end{itemize}

\subsection{PC Support Helpdesk Intern}{Expeditors International}{Jun. 2023 - Aug. 2023}
\begin{itemize}
    \item Managed high volumes of technical support tickets, providing efficient IT solutions and support across various departments, reducing downtime.
    \item Built and imaged 20+ computers for Microsoft contractors, implementing standardized systems and maintaining security protocols.
    \item Collaborated with the CyberSecurity team to revamp VPN protocols, improving data protection and access control for remote workers.
\end{itemize}

\subsection{QA Tester I Intern}{Denali Advanced Integration}{Jul. 2019 - Sept. 2019}
\begin{itemize}
    \item Designed and executed test cases for T-Mobile applications, identifying and documenting critical bugs, ensuring high product reliability.
    \item Engaged in cross-team communication to escalate and resolve software issues, contributing to the successful delivery of high-quality software.
    \item Developed foundational expertise in quality assurance processes, enhancing skills in test automation and bug tracking tools.
\end{itemize}